\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{blindtext}
\usepackage{multicol}

\titleformat{\section}{\bfseries\Large}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\bfseries\large}{}{0em}{}
\titlespacing{\subsection}{0em}{0.25em}{0.5em}
\titleformat{\subsubsection}[runin]{\bf}{}{0em}{}
\titlespacing{\subsubsection}{0em}{0.25em}{1em}

\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries\theauthor}

\vspace{.25em}

nicholas.carabio@gmail.com $|$ (484)-319-7076 $|$ \href{https://github.com/nickChivas}{Github: nickChivas}
\end{center}
}

\setlength{\parindent}{0pt}
\newcommand{\bd}{\textbf}

\begin{document}

\title{Resume}
\author{NICHOLAS CARABIO}

\maketitle

\section{EDUCATION}
\subsection{Eberly College of Science, Pennsylvania State University}
\emph{Bachelors of Science in Mathematics (Graduate Study Option), Minor in Physics} \hfill 2023-2027
\begin{itemize}
  \setlength\itemsep{0in}
\item GPA: 3.61/4.00.
\end{itemize}
\paragraph{Relevant Coursework: } Object-Oriented Programming, Systems Programming,
Ordinary and Partial Differential Equations, General Physics I-IV

\section{RESEARCH / PROJECTS}
\subsection{From Theory to Code: Visualizations of Discrete Mathematics}
\begin{itemize}
  \setlength\itemsep{0in}
  \item  Honors option project supervised by Georgios Eleftherakis, Assosciate Professor of Computer Science,
  for the spring 2025 semester.
  \item Built a library of software with Java and JavaFX to visualize and make accessible 
  abstract concepts of discrete mathematics.
  \item Completed formalization and literature of the course curriculum. 
\end{itemize}

\section{EXPERIENCE}
\subsection{Regal Cinemas}
\emph{Floor Staff} \hfill 2022-2025
\begin{itemize}
  \setlength\itemsep{0in}
  \item Responsible for customer service and building maintenace tasks.
  \item Cooperated with coworkers to create an enjoyable moviegoing environment.
  \item Communicated issues between customers and management.
\end{itemize}

\section{HONORS}
\subsection{Jane E. Cooper Honors Scholar}
\begin{itemize}
  \setlength\itemsep{0in}
  \item Member of the Penn State Brandywine honors program from 2023 to 2025.
  \item Selected to present my speech for a public speaking course at the fall 2023 Honors Symposium.
\end{itemize}

\section{TECHNICAL SKILLS} 
\begin{multicols*}{2}
\textbf{Programming Languages:} Python, Java, C \\
\textbf{Developer Tools:} Git, UNIX \\
\textbf{Markup Languages:} \LaTeX , Markdown \\

\columnbreak
\textbf{Microsoft Office Suite:} Microsoft Word, Microsoft Excel, Microsoft Powerpoint, Microsoft Teams \\
\textbf{Adobe Creative Cloud:} Adobe Photoshop, Adobe Premier Pro, Adobe Illustrator
\end{multicols*}

\end{document}